---
title: "financialization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## check NAs for dependent variables

Read data. 
oecd_percent.csv is produced by oecd.ipynb on April 26.

```{r}
library(data.table)
df <- fread('~/Projects/financialization/oecd_percent.csv')
df$V1 <- NULL
```

Keep only observations from 1970.
1954 obs in total.
```{r}
library(tidyverse)
df <- df %>%
  filter(Year >= 1970)
```

### Value-added in financial corporations
Produce va_na for the dependent variable of value added. 
The missing values are mainly from 1970-1994.
```{r}
table(is.na(df$DV_VA))
va_na <- df[is.na(df$DV_VA),]
table(va_na$Country)
table(va_na$Year)
```

### DV_debt
Produce va_na for the dependent variable of value added. 
The missing values are mainly from 1970-1994. This is close to DV_VA
```{r}
table(is.na(df$DV_debt))
va_na <- df[is.na(df$DV_debt),]
table(va_na$Country)
table(va_na$Year)
```

## explore imf data

### WEO
```{r}
weo <- fread('/Users/zhou-yimang/Projects/financialization/weo.csv', header = TRUE)
```
- Find no replacement of DV_VA, DV_debt, or DV_nonfinance in WEO

### IFS
International Financial Statistics
http://data.imf.org/?sk=4C514D48-B6BA-49ED-8AB9-52B0C1A0179B
```{R}
library(data.table)
library(tidyverse)
ifs <- fread('~/Projects/financialization/ifs.csv', header = TRUE,  fill=TRUE)
as.data.frame(table(ifs$`Indicator Name`)) -> ifs_indicator
write.csv(ifs_indicator, '~/Projects/financialization/ifs_indicator.csv')
```
- Find no replacement of DV_VA, DV_debt, or DV_nonfinance in ifs
- IFS is mainly a database for policies

