---
title: "model"
output: html_document
---
```{r}
# install.packages("pacman")
library(pacman)
p_load(data.table, tidyverse, Hmisc, Matrix, lfe, plm, dynlm, car, lmtest, tseries, broom, knitr)
```

## 0. Read the database

Keep only 1960-2018 variables
2006 observations, 47 variables

```{r}
library(tidyverse)
oecd <- read.csv("data_processing/oecd_year1960_2018.csv")
oecd$X <- NULL
oecd %>%
  filter(Year >= 1960) -> oecd
colnames(oecd)
```

### 0.1 Augmented Dickey-Fuller (ADF) test for Unit Root

http://www.econ.uiuc.edu/~econ508/R/e-ta8_R.html <br/>
"The Dickey-Fuller test tests the null hypothesis that a unit root is present in an autoregressive model. The alternative hypothesis is different depending on which version of the test is used, but is usually stationarity and trend-stationary." (wikipeida) <br/>
A unit root is present if $\rho = 1$ in $y_{t} = \rho y_{t-1}+u_{t}$.

Define adf function
```{r}
"adf" <- function(x,k = 0, int = TRUE, trend = FALSE){
# NB:  returns conventional lm summary so p-values for adf test are wrong!
    require(dynlm)
    dx <- diff(x)
    formula <- paste("dx ~ L(x)")
    if(k > 0)
        formula <- paste(formula," + L(dx,1:k)")
    if(trend){
        s <- time(x)
        t <- ts(s - s[1],start = s[1],freq = frequency(x))
        formula <- paste(formula," + t")
        }
    if(!int) formula <- paste(formula," - 1")
    summary(dynlm(as.formula(formula)))
}
```

ADF test for each country
Generate adf_test() function, the strategy is:
1. extract the column of independent variable X from df
2. for a certain country C, use adf() function to calculate the augmented Dickey-Fuller statistic for rejecting non-stationarity
3. combine the results from all countries together and report

```{r}
adf_test <- function(df, x, k = k){
   list<- c("country","lx_t")
   df %>%
     select(Country, Year, x) -> iv
   iv <- na.omit(iv)
   iv$Country <- as.character(iv$Country)
   country <- data.frame(table(iv$Country))[,1]
   for(i in 1:length(country)){
     countryname = as.character(country[i])
     temp <- iv %>%
       filter(Country == countryname)
     adf_iv <- ts(temp[,3])
     adf(adf_iv, k = k, int = T, trend = T) -> adf_model
     adf_model$coefficient[2,3] -> lx_t
     newrow <- c(countryname, lx_t)
     list <- rbind(list, newrow)
   }
   print(list)
}
```

for example, the results for testing IV_lendingplus in va <br/>
The Dickey-Fuller statistics should be about -2 with 0.05 confidence level <br/>
It is clear that the non-stationarity hypothesis should be rejected for all countries except Netherland. 
```{r}
adf_test(oecd,"IV_lendingplus",1)
```

```{r}
adf_test(oecd,"IV_gov_expplus",1)
```

```{r}
adf_test(oecd,"IV_trade_balanceplus",1)
```

```{r}
adf_test(oecd,"IV_fdi_outflowplus",1)
```

### 0.2 Cointegration: Phillips-Ouliaris test

```{r}
library(tseries)
po.test(as.matrix(cbind(oecd$DV_VAplus, oecd$IV_lendingplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_VAplus, oecd$IV_gov_expplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_VAplus, oecd$IV_trade_balanceplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_VAplus, oecd$IV_fdi_outflowplus), demean=FALSE))

po.test(as.matrix(cbind(oecd$DV_nfc_lsplus, oecd$IV_lendingplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_nfc_lsplus, oecd$IV_gov_expplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_nfc_lsplus, oecd$IV_trade_balanceplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_nfc_lsplus, oecd$IV_fdi_outflowplus), demean=FALSE))

po.test(as.matrix(cbind(oecd$DV_hh_lsplus, oecd$IV_lendingplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_hh_lsplus, oecd$IV_gov_expplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_hh_lsplus, oecd$IV_trade_balanceplus), demean=FALSE))
po.test(as.matrix(cbind(oecd$DV_hh_lsplus, oecd$IV_fdi_outflowplus), demean=FALSE))
```


## 1. Model 1: DV_VAplus

Create a new dataframe (va) with selected variables.<br/>
996 observations with 21 variables

### 1.0 Data Clean
```{r}
oecd %>%
dplyr::select(Country, Year, DV_VAplus, IVlag1_DV_VAplus,
              IV_lendingplus, IV_gov_expplus, IV_trade_balanceplus, IV_fdi_outflowplus, 
              IV_lendingplus_lag1, IV_lendingplus_lag2, IV_gov_expplus_lag1, IV_gov_expplus_lag2,
              IV_trade_balanceplus_lag1, IV_trade_balanceplus_lag2, IV_fdi_outflowplus_lag1, 
              IV_fdi_outflowplus_lag2, C_m2plus, C_NFLplus, C_REERplus, C_cpiplus, C_gdpplus) -> va
va[is.na(va)] <- 0
aggregate(. ~ Country + Year, data = va, sum) -> va
va[va==0] <- NA
va <- va[!is.na(va$DV_VAplus),]
```

### 1.1 Fixed effect model (plm)

```{r}
library(Matrix)
library(plm)
library(car)
library(lmtest)

m1  <- plm(DV_VAplus ~  IVlag1_DV_VAplus + 
                        IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                        IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                        IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                        C_m2plus + C_REERplus + C_cpiplus + C_gdpplus, 
          data = va, model = 'within',
          effect = 'twoways', index = c('Country', 'Year'))
summary(m1)

# PCSE
summary(m1, vcovBK)

# Durbin-Watson Statistics
pdwtest(m1)
```

#### Hausman test
```{r}
m1_re  <- plm(DV_VAplus ~  IVlag1_DV_VAplus + 
                        IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                        IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                        IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                        C_m2plus + C_REERplus + C_cpiplus + C_gdpplus, 
          data = va, model = 'random')
phtest(m1, m1_re)
```

### 1.2 LSDV model

```{r}
library(Matrix)
library(plm)
library(car)
library(lmtest)

m1_lsdv  <- lm(DV_VAplus ~  IVlag1_DV_VAplus + 
                        IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                        IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                        IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                        C_m2plus + C_REERplus + C_cpiplus + C_gdpplus + Country, data = va)
summary(m1_lsdv)
```

#### F-test for significance of one-way FE model

```{r}
library(car)
m1_lsdv %>% linearHypothesis(c("CountryBrazil = 0",
                   "CountryCanada = 0", 
                   "CountryChile = 0", 
                   "CountryChina (People's Republic of) = 0",
                   "CountryDenmark = 0", 
                   "CountryHungary = 0", 
                   "CountryIceland = 0",
                   "CountryIsrael = 0", 
                   "CountryJapan = 0", 
                   "CountryKorea = 0",
                   "CountryMexico = 0", 
                   "CountryNew Zealand = 0", 
                   "CountryNorway = 0",
                   "CountryPoland = 0", 
                   "CountrySouth Africa = 0", 
                   "CountrySweden = 0",
                   "CountrySwitzerland = 0", 
                   "CountryTurkey = 0", 
                   "CountryUnited Kingdom = 0",
                   "CountryUnited States = 0"))
```


## 2. Model 2: DV_nfc_lsplus

### 2.0 A similar method to clean data
```{r}
oecd %>%
dplyr::select(Country, Year, DV_nfc_lsplus, IVlag1_DV_nfc_lsplus,
              IV_lendingplus, IV_gov_expplus, IV_trade_balanceplus, IV_fdi_outflowplus,
              IV_lendingplus_lag1,IV_lendingplus_lag2, IV_gov_expplus_lag1,IV_gov_expplus_lag2,
              IV_trade_balanceplus_lag1, IV_trade_balanceplus_lag2, IV_fdi_outflowplus_lag1,
              IV_fdi_outflowplus_lag2, C_m2plus, C_NFLplus, C_REERplus, C_cpiplus, C_gdpplus) -> nfc
nfc[is.na(nfc)] <- 0
aggregate(. ~ Country + Year, data = nfc, sum) -> nfc
nfc[nfc ==0] <- NA
nfc <- nfc[!is.na(nfc$DV_nfc_lsplus),]
```

### 2.1 Fixed effect model (plm)

```{r}
library(Matrix)
library(plm)

m2  <- plm(DV_nfc_lsplus ~      IVlag1_DV_nfc_lsplus +
                        IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                        IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                        IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                        C_m2plus + C_REERplus + C_cpiplus + C_gdpplus, 
          data = nfc, model = 'within',
          effect = 'twoways', index = c('Country', 'Year'))
summary(m2)

# PCSE
summary(m2, vcovBK)

# Durbin-Watson statistics
pdwtest(m2)
```

#### Hausman test
```{r}
m2_re  <- plm(DV_nfc_lsplus ~      IVlag1_DV_nfc_lsplus +
                        IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                        IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                        IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                        C_m2plus + C_REERplus + C_cpiplus + C_gdpplus, 
          data = nfc, model = 'random')
phtest(m2, m2_re)
```

### 2.2 LSDV model

```{r}
library(Matrix)
library(plm)
library(car)
library(lmtest)

m2_lsdv  <- lm(DV_nfc_lsplus ~      IVlag1_DV_nfc_lsplus +
                        IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                        IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                        IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                        C_m2plus + C_REERplus + C_cpiplus + C_gdpplus + Country, data = nfc)
summary(m2_lsdv)
```

#### F-test for significance of one-way FE model

```{r}
library(car)
m2_lsdv %>% linearHypothesis(c("CountryBrazil = 0",
                   "CountryCanada = 0", 
                   "CountryChile = 0", 
                   "CountryChina (People's Republic of) = 0",
                   "CountryDenmark = 0", 
                   "CountryHungary = 0", 
                   "CountryIceland = 0",
                   "CountryIsrael = 0", 
                   "CountryJapan = 0", 
                   "CountryKorea = 0",
                   "CountryMexico = 0", 
                   "CountryNew Zealand = 0", 
                   "CountryNorway = 0",
                   "CountryPoland = 0", 
                   "CountrySouth Africa = 0", 
                   "CountrySweden = 0",
                   "CountrySwitzerland = 0", 
                   "CountryTurkey = 0", 
                   "CountryUnited Kingdom = 0",
                   "CountryUnited States = 0"))
```


## 3. Model 3: DV_hh_lsplus

### 3.0 A similar method to clean data

```{r}
oecd %>%
dplyr::select(Country, Year, DV_hh_lsplus, IVlag1_DV_hh_lsplus,
              IV_lendingplus, IV_gov_expplus, IV_trade_balanceplus, IV_fdi_outflowplus,
              IV_lendingplus_lag1,IV_lendingplus_lag2, IV_gov_expplus_lag1,IV_gov_expplus_lag2,
              IV_trade_balanceplus_lag1, IV_trade_balanceplus_lag2, IV_fdi_outflowplus_lag1,
              IV_fdi_outflowplus_lag2, C_m2plus, C_NFLplus, C_REERplus, C_cpiplus, C_gdpplus) -> hh
hh[is.na(hh)] <- 0
aggregate(. ~ Country + Year, data = hh, sum) -> hh
hh[hh ==0] <- NA
hh <- hh[!is.na(hh$DV_hh_lsplus),]
```

### 3.1 Fixed effect model (plm) 

```{r}
library(Matrix)
library(plm)

m3 <- plm(DV_hh_lsplus~ IVlag1_DV_hh_lsplus +
                         IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                         IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                         IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                         C_m2plus + C_REERplus + C_cpiplus + C_gdpplus, 
          data = hh, model = 'within',
          effect = 'twoways', index = c('Country', 'Year'))
summary(m3)

# PCSE
summary(m3, vcovBK)

# Dubin-Watson Statistics
pdwtest(m3)
```

#### Hausman test
```{r}
m3_re  <- plm(DV_hh_lsplus~ IVlag1_DV_hh_lsplus +
                         IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                         IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                         IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                         C_m2plus + C_REERplus + C_cpiplus + C_gdpplus, 
          data = hh, model = 'random')

summary(m3_re, vcovBK)
phtest(m3, m3_re)
pdwtest(m3_re)
```

### 3.2 LSDV model

```{r}
library(Matrix)
library(plm)
library(car)
library(lmtest)

m3_lsdv  <- lm(DV_hh_lsplus~ IVlag1_DV_hh_lsplus +
                         IV_lendingplus + IV_lendingplus_lag1 + IV_lendingplus_lag2 + 
                         IV_gov_expplus + IV_gov_expplus_lag1 + IV_gov_expplus_lag2 +
                         IV_trade_balanceplus + IV_trade_balanceplus_lag1 + IV_trade_balanceplus_lag2 +                                     IV_fdi_outflowplus + IV_fdi_outflowplus_lag1 + IV_fdi_outflowplus_lag2 +
                         C_m2plus + C_REERplus + C_cpiplus + C_gdpplus + Country, data = hh)
summary(m3_lsdv)
```

#### F-test for significance of one-way FE model

```{r}
library(car)
m3_lsdv %>% linearHypothesis(c("CountryBrazil = 0",
                   "CountryCanada = 0", 
                   "CountryChile = 0", 
                   "CountryChina (People's Republic of) = 0",
                   "CountryDenmark = 0", 
                   "CountryHungary = 0", 
                   "CountryIceland = 0",
                   "CountryIsrael = 0", 
                   "CountryJapan = 0", 
                   "CountryKorea = 0",
                   "CountryMexico = 0", 
                   "CountryNew Zealand = 0", 
                   "CountryNorway = 0",
                   "CountryPoland = 0", 
                   "CountrySouth Africa = 0", 
                   "CountrySweden = 0",
                   "CountrySwitzerland = 0", 
                   "CountryTurkey = 0", 
                   "CountryUnited Kingdom = 0",
                   "CountryUnited States = 0"))
```