---
title: "Model_v2.0"
author: "Yuemin Li and Yimang Zhou"
date: "4/30/2021"
output:
  pdf_document: default
  html_document: default
---

- A final version close to the paper.
- Rmarkdown for the paper should use model results from this version.
- The last version is Model_v1.8

```{r}
if (!require("pacman")) install.packages("pacman")
p_load(data.table, tidyverse, Hmisc, Matrix, lfe, plm, dynlm, car, lmtest, tseries, broom, knitr,
       pcse, ecm)
```

## 0. Data Preprocessing

Read the data and drop obs prior to 1960 (this step is not necessary).

```{r}
df <- read.csv("../data_processing/financialization_df.csv")
df$X <- NULL
df <- df %>%
      filter(Year >= 1960) 
colnames(df)
df[df==0] <- NA
df <- df[order(df$Country, df$Year),]

```

The data has already been preprocessed in other documents but requires further preprocessing. 

```{r}
# generate IV_fdi_net_pc and its lagged variables
df <- df %>%
  group_by(Country) %>%
  mutate(IV_fdi_net_lag1 = dplyr::lag(IV_fdi_net,k=1)) %>%
  mutate(IV_fdi_net_pc = (IV_fdi_net-IV_fdi_net_lag1)/IV_fdi_net_lag1*100) %>%
  mutate(IV_fdi_net_pc_lag1 = dplyr::lag(IV_fdi_net_pc,k=1)) %>%
  mutate(IV_fdi_net_pc_lag2 = dplyr::lag(IV_fdi_net_pc,k=2)) %>%
  ungroup()
# drop the inf values 
turn_na <- function(a){
  a[abs(a)>10^10] <- NA
  a
}
for(i in 2:length(df)){
  df[,i] <- lapply(df[,i], turn_na)
}

model_country <- c("Australia", "Austria", "Belgium", "Brazil", "Canada",
                   "Chile", "China", "Denmark", "Finland", "France",
                   "Germany", "Greece", "Hungary", "Iceland", "Ireland",
                   "Israel","Italy", "Japan", "Korea", "Mexico",
                   "Netherlands", "New Zealand", "Norway", "Poland", "Portugal",
                   "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom",
                   "United States")
df_model <- df[df$Country %in% model_country,]
```

We also make the dataframes including only the obs for each model.


```{r}
va_df <- df_model %>%
  select(DV_VA_pc,DV_VA_pc_lag1, 
          IV_lending_pc, IV_lending_pc_lag1,
          IV_gov_exp_pc, IV_gov_exp_pc_lag1,
          IV_trade_balance_pc, IV_trade_balance_pc_lag1,                           
          IV_fdi_net_pc, IV_fdi_net_pc_lag1,
          C_REER, C_wgdp, C_cpi, C_wgini,
         Country, Year)
va_df <- na.omit(va_df)

nfc_df <- df_model %>%
  select(DV_nfc_ls_pc,DV_nfc_ls_pc_lag1, 
          IV_lending_pc, IV_lending_pc_lag1,
          IV_gov_exp_pc, IV_gov_exp_pc_lag1,
          IV_trade_balance_pc, IV_trade_balance_pc_lag1,                           
          IV_fdi_net_pc, IV_fdi_net_pc_lag1,
          C_REER, C_wgdp, C_cpi, C_wgini,
          Country, Year)
nfc_df <- na.omit(nfc_df)

hh_df <- df_model %>%
  select(DV_hh_ls_pc,DV_hh_ls_pc_lag1, 
          IV_lending_pc, IV_lending_pc_lag1,
          IV_gov_exp_pc, IV_gov_exp_pc_lag1,
          IV_trade_balance_pc, IV_trade_balance_pc_lag1,                           
          IV_fdi_net_pc, IV_fdi_net_pc_lag1,
          C_REER, C_wgdp, C_cpi, C_wgini,
          Country, Year)
hh_df <- na.omit(hh_df)

```


## 1. Do the three levels of financialization co-occur and in the US only ?

This part attempts to select countries experience financialization since 1960. We determine it by test if an indicator of financialization (i.e., a dependent variable) is stationary by ADF tests. If the indicator is stationary in a country, it indicates that the country is not financialized during the period in this dimension.

"The Dickey-Fuller test tests the null hypothesis that a unit root is present in an autoregressive model. The alternative hypothesis is different depending on which version of the test is used, but is usually stationarity and trend-stationary." (wikipeida) 

A unit root is present if $\rho = 1$ in $y_{t} = \rho y_{t-1}+u_{t}$.
If the null hypothesis is not rejected, a unit root is present and the variable is not stationary. Instead, a variable is stationary if the null hypothesis is reject. 

Define adf function (http://www.econ.uiuc.edu/~econ508/R/e-ta8_R.html)

```{r}
"adf" <- function(x,k = 0, int = TRUE, trend = FALSE){
# NB:  returns conventional lm summary so p-values for adf test are wrong!
    require(dynlm)
    dx <- diff(x)
    formula <- paste("dx ~ L(x)")
    if(k > 0)
        formula <- paste(formula," + L(dx,1:k)")
    if(trend){
        s <- time(x)
        t <- ts(s - s[1],start = s[1],freq = frequency(x))
        formula <- paste(formula," + t")
        }
    if(!int) formula <- paste(formula," - 1")
    summary(dynlm(as.formula(formula)))
}
```


ADF test for each country
Generate adf_test() function, the strategy is:
1. extract the column of independent variable X from df
2. for a certain country C, use adf() function to calculate the augmented Dickey-Fuller statistic for rejecting non-stationarity
3. combine the results from all countries together and report

```{r}
adf_test <- function(df, x, k = k){
   result <- data.frame(country = c(),
                        lx_t = c(),
                        lx_p = c(),
                        stationarity = c())
   df %>%
     select(Country, Year, x) -> iv
   iv <- na.omit(iv)
   iv$Country <- as.character(iv$Country)
   country <- data.frame(table(iv$Country))[,1]
   for(i in 1:length(country)){
     countryname = as.character(country[i])
     temp <- iv %>%
       filter(Country == countryname)
     adf_iv <- ts(temp[,3])
     adf(adf_iv, k = k, int = T, trend = T) -> adf_model
     adf_model$coefficient[2,3] -> lx_t
     adf_model$coefficient[2,4] -> lx_p
     stationarity = c()
     stationarity[lx_p < 0.05] <- "stationarity"
     stationarity[lx_p > 0.05] <- "non-stationarity"
     newrow <- c(countryname, lx_t, lx_p, stationarity)
     result <- rbind(result, newrow)
   }
   colnames(result) <- c("country","lx_t","lx_p","stationarity")
   print(result)
}
```


```{r}
VA_adf <- adf_test(df, "DV_VA",1)
nfc_adf <- adf_test(df, "DV_nfc_ls",1)
hh_adf <- adf_test(df, "DV_hh_ls",1)
```

Hypothesis 1: The three levels of financialization do not co-occur in all countries. 

Compare the varieties of financialization among different countries

First, many countries find some kind of financialization. Only a few countries do not witness financialization in all the three levels (Estonia, Germany, Luxembourg).

Second, only a few countries find all the three levels of financialization (Australia, Israel, Italy, Slovak). Even in the U.S., financialization shows only in the level of the market and corporation. In most countries, the three levels of financialization do not co-occur.

```{r}
variety <- merge(VA_adf, nfc_adf, by = "country", all.y = T)
variety <- merge(variety, hh_adf, by = "country", all.y = T)
variety <- select(variety,
                  country, stationarity.x, stationarity.y, stationarity)
variety <- variety[,c("country", "stationarity.x", "stationarity.y", "stationarity")]
colnames(variety) <- c("country", "va", "nfc", "hh")
variety
```

## 2. PCSE Models

Correlation matrix

```{r}
cor_df <- df_model %>%
  select(DV_VA_pc,DV_nfc_ls_pc,DV_hh_ls_pc,
         IV_lending_pc, IV_gov_exp_pc,IV_trade_balance_pc,IV_fdi_net_pc)
cor_mat <- cor(cor_df, use = 'na')
cor_mat[upper.tri(cor_mat)] <- NA
cor_mat
write.csv(cor_mat, '../table_and_figure/cor_mat.csv')
```

Three PCSE models

```{r}
# model 1
va_df$Country <- as.factor(va_df$Country)
m1_lm <- lm(DV_VA_pc ~  DV_VA_pc_lag1 + 
              IV_lending_pc + IV_lending_pc_lag1+ 
              IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
              IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                             
              IV_fdi_net_pc + IV_fdi_net_pc_lag1 + 
              C_REER + C_wgdp + C_cpi + C_wgini  + 
              as.factor(Year) + as.factor(Country), 
            data = va_df)
m1_pcse <- pcse(m1_lm, groupN = va_df$Country, groupT = va_df$Year, pairwise = TRUE)

# model 2
nfc_df$Country <- as.factor(nfc_df$Country)
m2_lm <- lm(DV_nfc_ls_pc ~  DV_nfc_ls_pc_lag1 + 
              IV_lending_pc + IV_lending_pc_lag1+ 
              IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
              IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                             
              IV_fdi_net_pc + IV_fdi_net_pc_lag1 + 
              C_REER + C_wgdp + C_cpi + C_wgini  + 
              as.factor(Year) + as.factor(Country), 
            data = nfc_df)
m2_pcse <- pcse(m2_lm, groupN = nfc_df$Country, groupT = nfc_df$Year, pairwise = TRUE)

# model 3
hh_df$Country <- as.factor(hh_df$Country)
m3_lm <- lm(DV_hh_ls_pc ~  DV_hh_ls_pc_lag1 + 
              IV_lending_pc + IV_lending_pc_lag1+ 
              IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
              IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                             
              IV_fdi_net_pc + IV_fdi_net_pc_lag1 + 
              C_REER + C_wgdp + C_cpi + C_wgini  + 
              as.factor(Year) + as.factor(Country), 
            data = hh_df)
m3_pcse <- pcse(m3_lm, groupN = hh_df$Country, groupT = hh_df$Year, pairwise = TRUE)

summary(m1_pcse)
summary(m2_pcse)
summary(m3_pcse)
```

## 3. Diagnosis

### 3.1 Phillips-Ouliaris test of Cointegration

"Cointegration is a technique used to find a possible correlation between time series processes in the long term. Nobel laureates Robert Engle and Clive Granger introduced the concept of cointegration in 1987. The most popular cointegration tests include Engle-Granger, the Johansen Test, and the Phillips-Ouliaris test."

The null hypothesis of Phillips-Ouliaris test is that x not cointegrated.In all tests. 

In all tests below, null hypotheses are rejected and suggest that the cointegration exists between dependent and independent variables.

```{r}
library(tseries)
po.test(as.matrix(cbind(va_df$DV_VA_pc, va_df$IV_lending_pc), demean=FALSE)) -> po_va_lending
po.test(as.matrix(cbind(va_df$DV_VA_pc, va_df$IV_gov_exp_pc), demean=FALSE)) -> po_va_exp
po.test(as.matrix(cbind(va_df$DV_VA_pc, va_df$IV_trade_balance_pc), demean=FALSE)) -> po_va_trade
po.test(as.matrix(cbind(va_df$DV_VA_pc, va_df$IV_fdi_net_pc), demean=FALSE)) -> po_va_fdi

po_va <- rbind(as.numeric(po_va_lending[1]), as.numeric(po_va_exp[1]), 
               as.numeric(po_va_trade[1]), as.numeric(po_va_fdi[1]))
po_va

po.test(as.matrix(cbind(nfc_df$DV_nfc_ls_pc, nfc_df$IV_lending_pc), demean=FALSE)) -> po_nfc_lending
po.test(as.matrix(cbind(nfc_df$DV_nfc_ls_pc, nfc_df$IV_gov_exp_pc), demean=FALSE)) -> po_nfc_exp
po.test(as.matrix(cbind(nfc_df$DV_nfc_ls_pc, nfc_df$IV_trade_balance_pc), demean=FALSE)) -> po_nfc_trade
po.test(as.matrix(cbind(nfc_df$DV_nfc_ls_pc, nfc_df$IV_fdi_net_pc), demean=FALSE)) -> po_nfc_fdi

po_nfc <- rbind(as.numeric(po_nfc_lending[1]), as.numeric(po_nfc_exp[1]), 
               as.numeric(po_nfc_trade[1]), as.numeric(po_nfc_fdi[1]))

po_nfc

po.test(as.matrix(cbind(hh_df$DV_hh_ls_pc, hh_df$IV_lending_pc), demean=FALSE)) -> po_hh_lending
po.test(as.matrix(cbind(hh_df$DV_hh_ls_pc, hh_df$IV_gov_exp_pc), demean=FALSE)) -> po_hh_exp
po.test(as.matrix(cbind(hh_df$DV_hh_ls_pc, hh_df$IV_trade_balance_pc), demean=FALSE)) -> po_hh_trade
po.test(as.matrix(cbind(hh_df$DV_hh_ls_pc, hh_df$IV_fdi_net_pc), demean=FALSE)) -> po_hh_fdi

po_hh <- rbind(as.numeric(po_hh_lending[1]), as.numeric(po_hh_exp[1]), 
               as.numeric(po_hh_trade[1]), as.numeric(po_hh_fdi[1]))

po_hh
```

#### 3.2 Test of Cross-sectional Dependence (Contemporaneous Correlations)

Panel data can be subject to pervasive cross-sectional dependence, whereby all units in the same cross-section are correlated. This is usually attributed to the effect of some unobserved common factors, common to all units and affecting each of them, although possibly in different ways. 

"According to Baltagi, cross-sectional dependence is a problem in macro panels with long time series. This is not much of a problem in micro panels (few years and large number of cases). 
The null hypothesis in the B-P/LM and Pasaran CD tests of independence is that residuals across entities are not correlated. B-P/LM and Pasaran CD (cross-sectional dependence) tests are used to test whether the residuals are correlated across entities*. Cross-sectional dependence can lead to bias in tests results (also called contemporaneous correlation). "

Package ‘panelAR’ is used here to test the cross-sectional dependency but the package is problematic.

The below tests suggest heteroskedasticity exists for fixed-effect models.

```{r}
m1_fe  <- plm(DV_VA_pc ~  DV_VA_pc_lag1 + 
              IV_lending_pc + IV_lending_pc_lag1+ 
              IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
              IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                             
              IV_fdi_net_pc + IV_fdi_net_pc_lag1 + 
              C_REER + C_wgdp + C_cpi + C_wgini,
          data = va_df, model = 'within',
          effect = 'twoways', index = c('Country', 'Year'))

m2_fe  <- plm(DV_nfc_ls_pc ~  DV_nfc_ls_pc_lag1 + 
              IV_lending_pc + IV_lending_pc_lag1+ 
              IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
              IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                             
              IV_fdi_net_pc + IV_fdi_net_pc_lag1 + 
              C_REER + C_wgdp + C_cpi + C_wgini,
          data = nfc_df, model = 'within',
          effect = 'twoways', index = c('Country', 'Year'))


m3_fe  <- plm(DV_hh_ls_pc ~  DV_hh_ls_pc_lag1 + 
              IV_lending_pc + IV_lending_pc_lag1+ 
              IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
              IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                             
              IV_fdi_net_pc + IV_fdi_net_pc_lag1 + 
              C_REER + C_wgdp + C_cpi + C_wgini,
          data = hh_df, model = 'within',
          effect = 'twoways', index = c('Country', 'Year'))

pcdtest(m1_fe, test = c("lm"))
pcdtest(m2_fe, test = c("lm"))
pcdtest(m3_fe, test = c("lm"))

```

#### 3.3 Testing for unit roots/stationarity

The result rejects the null hypothesis that non-stationarity exists. 

```{r}
p_load(fBasics,fUnitRoots)
if (!require("punitroots"))install.packages("punitroots", repos="http://R-Forge.R-project.org")
if (!require("CADFtest"))install.packages("CADFtest")
#install.packages("ua")
library(punitroots)

padf <- function(df, x){
  df %>%
    select(Country, Year, x) -> iv
  iv <- na.omit(iv)
  result = pCADFtest(Y=iv, max.lag.y = 5, criterion = "AIC", crosscorr=0.10)
  print(result)
}

padf(va_df, "DV_VA_pc")
padf(nfc_df, "DV_nfc_ls_pc")
padf(hh_df, "DV_hh_ls_pc")
```

#### 3.4 test for heteroskedasticity 

The null hypothesis for the Breusch-Pagan test is homoskedasticity

The test below rejects the null hypothesis and suggests the presence of heteroskedasticity.
```{r}
library(lmtest)
bptest(DV_VA_pc ~  DV_VA_pc_lag1 + 
                        IV_lending_pc + IV_lending_pc_lag1 + 
                        IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
                        IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                           
                        IV_fdi_net_pc + IV_fdi_net_pc_lag1 +
                        C_REER + C_wgdp + C_cpi + C_wgini + factor(Country), data=va_df, studentize=F)


```

The test below rejects the null hypothesis and suggests the presence of heteroskedasticity.

```{r}
bptest(DV_nfc_ls_pc ~  DV_nfc_ls_pc_lag1 + 
                        IV_lending_pc + IV_lending_pc_lag1 + 
                        IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
                        IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                           
                        IV_fdi_net_pc + IV_fdi_net_pc_lag1 +
                        C_REER + C_wgdp + C_cpi + C_wgini + factor(Country), data=nfc_df, studentize=F)


```
The test below rejects the null hypothesis and suggests the presence of heteroskedasticity.

```{r}
bptest(DV_hh_ls_pc ~  DV_hh_ls_pc_lag1 + 
                        IV_lending_pc + IV_lending_pc_lag1 + 
                        IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
                        IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                           
                        IV_fdi_net_pc + IV_fdi_net_pc_lag1 +
                        C_REER + C_wgdp + C_cpi + C_wgini + factor(Country), data=hh_df, studentize=F)


```

### 3.5 Breusch-Godfrey test Test for autocorrelation

```{r}
lmtest::bgtest(DV_VA_pc ~  DV_VA_pc_lag1 + 
                        IV_lending_pc + IV_lending_pc_lag1 + 
                        IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
                        IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                           
                        IV_fdi_net_pc + IV_fdi_net_pc_lag1 +
                        C_REER + C_wgdp + C_cpi + C_wgini + factor(Country), data=va_df)

lmtest::bgtest(DV_nfc_ls_pc ~  DV_nfc_ls_pc_lag1 + 
                        IV_lending_pc + IV_lending_pc_lag1 + 
                        IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
                        IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                           
                        IV_fdi_net_pc + IV_fdi_net_pc_lag1 +
                        C_REER + C_wgdp + C_cpi + C_wgini + factor(Country), data=nfc_df)

lmtest::bgtest(DV_hh_ls_pc ~  DV_hh_ls_pc_lag1 + 
                        IV_lending_pc + IV_lending_pc_lag1 + 
                        IV_gov_exp_pc + IV_gov_exp_pc_lag1 + 
                        IV_trade_balance_pc + IV_trade_balance_pc_lag1 +                           
                        IV_fdi_net_pc + IV_fdi_net_pc_lag1 +
                        C_REER + C_wgdp + C_cpi + C_wgini + factor(Country), data=hh_df)

```

## 4. Robustness: ECM

```{r}
p_load('ecm')
xtr <- va_df[c('IV_lending_pc', 'IV_gov_exp_pc', 'IV_trade_balance_pc', 'IV_fdi_net_pc','C_REER', 'C_wgdp', 'C_cpi', 'C_wgini')]
xeq <- va_df[c('IV_lending_pc', 'IV_gov_exp_pc', 'IV_trade_balance_pc', 'IV_fdi_net_pc')]
m1_ecm <- ecm(va_df$DV_VA_pc, xeq, xtr, includeIntercept=TRUE)
lmtest::bptest(m1_ecm)
lmtest::bgtest(m1_ecm)
lmtest::coeftest(m1_ecm, vcov=sandwich::NeweyWest)

xtr <- nfc_df[c('IV_lending_pc', 'IV_gov_exp_pc', 'IV_trade_balance_pc', 'IV_fdi_net_pc','C_REER', 'C_wgdp', 'C_cpi', 'C_wgini')]
xeq <- nfc_df[c('IV_lending_pc', 'IV_gov_exp_pc', 'IV_trade_balance_pc', 'IV_fdi_net_pc')]
m2_ecm <- ecm(nfc_df$DV_nfc_ls_pc, xeq, xtr, includeIntercept=TRUE)
lmtest::bptest(m2_ecm)
lmtest::bgtest(m2_ecm)
lmtest::coeftest(m2_ecm, vcov=sandwich::NeweyWest)

xtr <- hh_df[c('IV_lending_pc', 'IV_gov_exp_pc', 'IV_trade_balance_pc', 'IV_fdi_net_pc','C_REER', 'C_wgdp', 'C_cpi', 'C_wgini')]
xeq <- hh_df[c('IV_lending_pc', 'IV_gov_exp_pc', 'IV_trade_balance_pc', 'IV_fdi_net_pc')]
m3_ecm <- ecm(hh_df$DV_hh_ls_pc, xeq, xtr, includeIntercept=TRUE)
lmtest::bptest(m3_ecm)
lmtest::bgtest(m3_ecm)
lmtest::coeftest(m3_ecm, vcov=sandwich::NeweyWest)

summary(m1_pcse)
summary(m2_pcse)
summary(m3_pcse)
```

```{r}
save.image("../data_model/model.RData")
```